Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
comment

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need to compute identity hypercoercion for the codomain when 
evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -JS
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -JS
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -JS
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        \\---\\
        Fixed. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

@@

@@

We use bisimulation to proof equivalence between the two machines.
The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations. We omit subscripts when there is no ambiguity.

@@

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{D} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeDCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
\end{proof}

>>>>

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need the codomain when evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -JS
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -JS
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -JS
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        }
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

@@

\todo[inline]{In the definition of values, there is a ``b'' in the fun
  case. I don't see any definitions of a nonterminal ``b''.
  Perhaps you meant ``e''. -JS}
\todo[inline]{In the grammars for values and pre-continuations,
   remove all the subscripts on c's and v's. -JS}
\todo[inline]{Change the syntax $(c,k)$ for continuations to
  $\langle c \rangle$ k. -JS}

@@

\todo[inline]{Give a high-level summary of the proof.
  The summary should be enough so that the reader knows a bit
  about why you introduce the various definitions below. -JS}

@@

\todo[inline]{``monoidic'' is not a word. -JS}

We use bisimulation to proof equivalence between the two machines.
\todo[inline]{Which two machines? -JS}
The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations. We omit subscripts when there is no ambiguity.

@@

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{D} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and monoidic,
	\[
	\judgeDCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{lemma}
\begin{proof}
  Immediately from Lemma~\ref{thm:surely-monoidic-reduce}.
  \todo[inline]{I'm guessing that you prove this lemma by induction,
    using Lemma~\ref{thm:surely-monoidic-reduce}.
    Proofs by induction are not ``immediate''. -JS}
\end{proof}
